Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-03-22 doc/JFM2022/OldStuff/reviews/ResponseToReviewer2.tex

To highlight both the similarity and difference between our JP vesicle and the lipid bilayer vesicle, we study (1) the hydrodynamics of a JP vesicle in various flow conditions to compare with the corresponding results for a lipid bilayer vesicle,
(2) we compute the friction between the two JP leaflet, and the permeability of a JP bilayer. We find that the permeability of a JP vesicle allows the total water content enclosed in the JP vesicle to reach an equilibrium value in a flow. We find that the JP vesicle is actually closer to a permeable vesicle, where the 2D vesicle has a constant perimeter but the enclosed area does not stay constant.

In terms of validation of our numerical results of JP vesicle of nanometer size, we have made comparison with the simulations of vesicle of the same size in the literature. For example we compare both the permeability and the inter-leaflet friction coefficient of a JP bilayer membrane with those of a lipid bilayer membrane. We also compare the critical shear rate for rupture between a JP vesicle and a lipid bilayer vesicle. We also compared the hydrodynamics of a JP vesicle and a lipid bilayer vesicle under various flowing conditions. These results are summarized
and re-organized in the revision with better clarity.

@@

Finally we provide a critical capillary number for rupture of a JP vesicle under a linear shear flow. The rupture of a lipid vesicle by a linear shear flow has been reported in experiments.  Our prediction of a critical capillary number and how it scales with various physical parameters of the individual Janus particle is, to our knowledge, not available in the literature. We hope that our results can motivate experimentalist (such as Charles Schroeder who has studied extreme deformation of a vesicle due to an imposed flow) and other theoreticians to study the dynamics of bilayer structures under extreme flowing conditions.

%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

\noindent
\comment{The abbreviation HAP is not defined in the text. I guess it stands for hydrophobic attraction potential.
}
\begin{itemize}
  \item Response: Thank you for noticing this oversight. 
  \item Change: The definition of HAP has been added at its first occurrence in Section 3.1. 
\end{itemize}

\noindent
\comment{$u$ is used for both the velocity and the solutions of the
Laplace equation. Please use another variable for the scalar function
$u$.}
\begin{itemize}
\item Response: The velocity ${\bf u}({\bf x})$ introduced in the mobility problem (eqn. (2.1)--(2.3)) is in bold face and of a vector form. The scalar solution function $u$ is the solution of the screened Laplace equation boundary value problem (eqn. (2.7)--(2.9)).
  We can see, however, how this might result in confusion. 
\item Change: In response to this point, we changed the scalar function $u$ to $\eta$ throughout the manuscript.
  The notation $\eta$ was used by Stjepan Marcelja to first pose the HAP formulation
  in Croatica Chemica Acta, 1977.
\end{itemize}

@@

\noindent
\comment{$\rho$ used in the HAP is not the same as the one used in the
mobility boundary integral equation. One is a decay length of the
attraction potential, while the second is the Euclidean distance between
two JPs.}
\begin{itemize}
  \item Response: We had used $\rho$ to denote the distance between source and
    target points in one of the layer potentials. This has been removed.

  \item Change: We now use $\rho$ to denote the HAP decay length and $\rho_0$ to
    denote the cutoff for the repulsion force.
\end{itemize}

\noindent
\comment{$\nu$ is used on multiple instances, sometimes as a normal
vector (see line 97 for example), and other times as some scalar
function (see line 203).}
\begin{itemize}
  \item Response: We thank the referee for this oversight.
  \item Change: We now reserve $\boldsymbol{\nu}$ for the normal vector and
    $w_i$ denote the scalar what we previously defined to be $\nu_i$.
\end{itemize}

\noindent
\comment{What is the bending modulus here? I guess that it is not a
direct input parameter in this model but rather a quantity that can be
deduced from other input parameters. If I am right then, what are these
parameters? And could you tune them if needed to simulate the effect of
the membrane stiffness? This can be important in some applications such
as rigidity-based microfluidic sorting devices.}
\begin{itemize}
\item Response: The Reviewer is correct that realistic bending moduli
  and other elastic parameters can be deduced from simulation data.
  At this point, however, we do not have any analytical connection between
  the input and moduli and inputs, other than some scaling relationships.
  Please see the next comment, though, regarding the bending and stretching
  moduli.
\item Change: In the beginning of Section 4.1,
  we now point out that such an empirical analysis was part of our previous work.  
\end{itemize}

\noindent
\comment{To compare the results with the existing literature, I would
suggest introducing the capillary number for vesicles as defined in
\url{https://doi.org/10.1016/j.crhy.2009.10.001}.}
\begin{itemize}
\item Response:  We thank the Reviewer for pointing out this intriguing connection. 
\item Change:  Reviewer 1 requested a parametric study of membrane rupture which
  we now supply in Section 4.2.3. There we take up the present Reviewer's
  suggestion and show how the critical rupture shear rate ties in with the capillary
  number, and then use the capillary number to derive an effective bending rigidity. 
\end{itemize}

\noindent
\comment{For both examples with the linear shear flow and the Poiseuille
flow, the area of the vesicle is not conserved and the relative error
with respect to the stress-free area increases with the increase of the
external stresses. It can reach roughly 7-8\% for the higher shear rate
in the shear flow example. This is quite significant. Do you have a way
to reduce this error to below 1\%? Note that in other numerical models
for vesicles (e.g.~\url{https://doi.org/10.1016/j.jcp.2008.11.036}),
both constant area and perimeter constraints are fulfilled even when the
vesicle is more deformed than the cases reported here.}
\begin{itemize}
\item Response: We thank the referee for this comment. For impermeable vesicles, the referee is correct about the numerical errors reported in the literature. However, the JP membrane is permeable and in our simulations we found that the
  JP vesicle needs time so the particles in the membrane can re-arrange themselves. During this process of rearrangement the JP bilayer membrane behaves as a permeable membrane as in Quaife, Gannon and Young (PRF 2021). For a JP vesicle in a linear shear flow with a shear rate of dimensionless shear $\chi = 0.002$ the enclosed area reaches a nearly constant value after $1$ $\mu$s. We would like to point out that this is not a numerical error, but a consequence of JP hydrodynamics that gives rise to membrane permeability.

### 2022-03-22 doc/JFM2022/OldStuff/main_jfm_orig.tex

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}

%
\usepackage[justification=justified]{caption}

@@

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}
\newcommand{\ReviewerOne}[1]{\textcolor{red}{#1}}
\newcommand{\ReviewerTwo}[1]{\textcolor{green}{#1}}
\newcommand{\ReviewerThree}[1]{\textcolor{magenta}{#1}}

@@

%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
\title{Two-Dimensional Hydrodynamics of a Janus Particle Vesicle}
%\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

@@

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact through a hydrophobic attraction potential 
  that leads to self-assembly into bilayer structures.   
  We adopt an efficient integral equation method for solving the screened
  Laplace equation for hydrophobic attraction and 
  for solving the mobility problem for hydrodynamic interactions. 
  The integral equation formulation accurately captures both interactions for near touched boundaries. 
  Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles.
  The results yield measurements of inter-monolayer friction, membrane permeability, 
  and at large shear rates, membrane rupture. 
  The simulations studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
  interactions between two Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
  particles vesicle is similar to the behaviour of an inextensible elastic vesicle membrane with permeability.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $\ReviewerTwo{\eta} = 1$ and blue is for $\ReviewerTwo{\eta} = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, \ReviewerOne{and} $A$ is the enclosed area\ReviewerOne{.}
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

In the present work, we extend the hybrid continuum model in~\cite{Fu20}
for the Janus suspension to incorporate the collective hydrodynamics of
a Janus suspension under various flows. The JP vesicles in our
simulations replicate  \ReviewerOne{well-known} vesicle hydrodynamics
such as tank-treading and inter-leaflet slippage in a shear flow and
migration in Poiseuille flow from continuum models. Furthermore we use
the hybrid continuum model to investigate permeability and rupture of a
bilayer membrane due to an imposed flow.  Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

%\cite{Brandner2019} used the coarse-grained force field with a lattice
%Boltzmann molecular dynamics to simulate the hydrodynamics of a
%nano-sized vesicle under a shear flow.  In MD simulations, the
%hydrodynamic interactions for the solvent phase are often approximated
%by an implicit solvent coarse-grained model.  In the present work, the
%hydrodynamic interactions come from the mobility problem for the Stokes
%equations for the incompressible, viscous solvent.

To simulate the hydrodynamics of Janus particles in Stokes flow,
we require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
%
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\ReviewerOne{the no-slip boundary condition}
\begin{align}
\label{eq:rigid_bc}
  \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$.
%Therefore, the no-slip boundary condition on each particle is
%
%
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i.
%\end{align}
%
%
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts: hydrophobic attraction
and repulsion. The hydrophobic attraction potential was introduced
by~\cite{Fu20} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
We model hydrophobic attraction by solving the screened Laplace equation
boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta \ReviewerTwo{\eta} + \ReviewerTwo{\eta} &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
\ReviewerTwo{\eta}(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
\label{eq:SLff}
\ReviewerTwo{\eta} &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that both $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho > 0$ is the decay length of attraction. The
forces and torques of attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}\ReviewerTwo{\eta}^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  \ReviewerTwo{\eta}|^2 \mathbf{I} - \nabla \ReviewerTwo{\eta}  \nabla \ReviewerTwo{\eta}^T\right)
\end{align}
is the hydrophobic stress tensor and $\gamma > 0$ is
the interfacial
tension.

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$.
Then, the total imposed force and torque
are
\begin{equation}
\label{eq:total_forces}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{equation}

\ReviewerThree{
The high-order interpolation-based quadrature rule used to compute the
nearly-singular integrals has been shown to accurately capture the
lubrication hydrodynamics in the narrow space between boundaries when
the repulsive potential $P$ gives a large steric
force~\citep{qua-bir2014}. In the simulations we adjust the spatial
resolution on the particle boundary to ensure that the lubrication
hydrodynamics is well resolved as in~\citep{qua-vee-you2019,
qua-gan-you2021}.
}
%

%%%% moved to new section 3.4

%\subsection{Time Marching}
%By solving the mobility problem, we obtain translational and angular
%velocities of the $N_b$-body system. 
%A second-order Adams-Bashforth
%scheme updates the particle positions and orientations. By including the
%repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
%when using a relatively large time step.

@@

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles
\ReviewerTwo{and empitically deduced realistic bending moduli, stretching moduli,
  and tilt moduli under reasonable assumptions for the input parameters.}
In the present work, we study JP vesicles in various background flows.
We also perform parametric studies of effective properties of the JP vesicles 
as a function of particle size and interaction strength.

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}
%
\usepackage[justification=justified]{caption}

@@

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
\title{Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential}
%\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

@@

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact through a hydrophobic attraction potential 
  that leads to self-assembly into bilayer structures.   
  We adopt an efficient integral equation method for solving the screened
  Laplace equation for hydrophobic attraction and 
  for solving the mobility problem for hydrodynamic interactions. 
  The integral equation formulation accurately captures both interactions for near touched boundaries. 
  Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles.
  The results yield measurements of inter-monolayer friction, membrane permeability, 
  and at large shear rates, membrane rupture. 
  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
  interactions in shear and extensional flows. The hydrodynamics of the Janus 
  particles vesicle replicate the behaviour of an inextensible elastic vesicle membrane.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $u = 1$ and blue is for $u = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, $A$ is the enclosed area, and $L$ is the arc
  length. Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

In the present work, we extend the hybrid continuum model in~\cite{Fu20}
for the Janus suspension to incorporate the collective hydrodynamics of
a Janus suspension under various flows. The JP vesicles in our
simulations replicate  well-know vesicle hydrodynamics such as
tank-treading and inter-leaflet slippage in a shear flow and migration
in Poiseuille flow from continuum models. Furthermore we use the hybrid
continuum model to investigate permeability and rupture of a bilayer
membrane due to an imposed flow.  Finally, we compare a pair of
interacting JP vesicles with a continuum model of a pair of vesicles.

\cite{Brandner2019} used the coarse-grained force field with a lattice
Boltzmann molecular dynamics to simulate the hydrodynamics of a
nano-sized vesicle under a shear flow.  In MD simulations, the
hydrodynamic interactions for the solvent phase are often approximated
by an implicit solvent coarse-grained model.  In the present work, the
hydrodynamic interactions come from the mobility problem for the Stokes
equations for the incompressible, viscous solvent.

We require a numerical method to avoid unphysical contact between rigid
Janus particles. Optimization-based contact methods introduce
constraints, such as enforcing a non-positive space-time interference
volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
methods do not introduce stiffness, but do require solving potentially
expensive nonlinear complementarity problems at each time step.
Repulsion-based contact methods, which we employ, introduce an
artificial repulsion force that increases in strength as two particles
approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
kab-qua-bir2018}). Strong repulsion forces can introduce numerical
stiffness, but with the presence of the hydrophobic forces, we maintain
contact-free suspensions with a relatively weak non-stiff repulsive
force.

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts: hydrophobic attraction
and repulsion. The hydrophobic attraction potential was introduced
by~\cite{Fu20} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
We model hydrophobic attraction by solving the screened Laplace equation
boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
\label{eq:SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that both $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho > 0$ is the decay length of attraction. The
forces and torques of attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor and $\gamma > 0$ is
the interfacial
tension.

The second part of the imposed forces and torques comes from repulsion
between proximal particles. Given a pair particles indexed with $i$ and
$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
define the repulsion force and torque
\begin{align}
  \label{eq:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
  \label{eq:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} 
    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{align}
The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
and~\eqref{eq:REPULtorque} ignore particles outside a
$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
prevent particle collisions. Then, the total imposed force and torque
are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Marching}
By solving the mobility problem, we obtain translational and angular
velocities of the $N_b$-body system. 
A second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
when using a relatively large time step.

@@

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles for
various particle shapes. In the present study, we fix the particle shape
and vary the background flows. Specifically, the particles are circular
disks with diameter $l_0 = 2.5$~nm. The boundary
conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle centre
and director respectively. The particle diameter is the thickness of
monolayers and the director points in the direction of the hydrophobic
side of the JP.
